### 2024-01-12 documentation/thesis/thesis_document.tex
more thesis

@@

The scope of the software library is to lay the foundation for the
systematic characterization of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customization possible at each step of the process. The
work aims to facilitate magnetic field characterization and improve the
exchange of data between different user groups. Complete documentation,
tutorials and tests will enable users to use the framework efficiently
and adapt it to their specific requirements. The application of the
developed framework for the characterization of different magnets and
the integration of magnetic field sensors serve as practical
applications and validation of the developed solution.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received. Since the presumed
\passthrough{\lstinline!primary!} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout branch
condition \passthrough{\lstinline!got pulse within 1000ms!} and this
becomes the \passthrough{\lstinline!primary!} sensor. This means that in
a chain of sensors there is exactly one
\passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
this automatically jumps to \passthrough{\lstinline!primary!} sensor
operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the
\passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
command. An important aspect of the implementation here was that there
is no numbering or sequence of the individual sensors. This means that
for the subsequent readout of the measurements, it is only important
that they are taken at the same interval across all sensors. The sensor
differentiation takes place later in the \gls{mrp}
\ref{software-readout-framework}-library by using the sensor \gls{id}.

@@

\hypertarget{library-requirements}{%
\section{Library requirements}\label{library-requirements}}

\hypertarget{concepts}{%
\subsection{Concepts}\label{concepts}}

\begin{itemize}
\tightlist
\item
  beispiele für projekte welche nur einzelne schnritte implementieren
\item
  so kann man sich auf die implementierung
\end{itemize}

\hypertarget{user-interaction-points}{%
\subsection{User interaction points}\label{user-interaction-points}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRPlib_COMPLETE_FLOW.png}
\caption{MRPlib COMPLETE FLOW \label{MRPlib_COMPLETE_FLOW.png}}
\end{figure}

\begin{itemize}
\tightlist
\item
  jeder schritt nach der DAQ basiert auf dem gleichen grundtyp datentyp
\item
  meta-daten werden bei jedem weiteren schritt hinzugeügt um
  nachverfolgbarkeit zu gewärleisten
\end{itemize}

@@

The library consists of various modules, which are divided into two
categories:

@@

An overview of these is given in the subchapters as the following. There
are also introductory examples which provide an overview of the basic
functions in the \passthrough{\lstinline!Examples!}\ref{examples}
section, as well as further examples in the online
documentation\cite{MagneticReadoutProcessingReadTheDocs}.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!additional\_data!} - Additional user-defined
  metadata
\item
  \passthrough{\lstinline!data!} - Measured values with value and
  measured value \gls{id}
\item
  \passthrough{\lstinline!measurement\_config!} - Information about the
  sensor used for measurement
\end{itemize}

@@

Each connected sensor is accessed via the text-based \gls{cli}, this is
initially the same for each sensor. The only identification feature is
the sensor \gls{id} by using the \passthrough{\lstinline!id!} command of
the sensor \gls{cli}.

@@

Immediately after starting the \passthrough{\lstinline!MRPProxy!}, the
\gls{id}s of all locally connected sensors are read out. These are
stored together with the class instance of the
\passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
possible to address a sensor directly using its \gls{id}.

@@

To realize this, a \gls{lut} was created in the previous steps, which
contains information regarding
\passthrough{\lstinline!requested capability!} -\textgreater{}
\passthrough{\lstinline!sensor!}-\gls{id} -\textgreater{}
\passthrough{\lstinline!physical sensor!} and allows the commands to be
routed.

@@

The \passthrough{\lstinline!extend commands using an id parameter!}
strategy is used for different sensors. Each command is extended on the
\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} by another
\gls{id} parameter, according to the following scheme:

@@

This allows the host to address individual sensors directly via their
specific \gls{id}.

@@

In general, a sensor can be connected using its specific system path or
the sensor-\gls{id} via the
\passthrough{\lstinline!MRPHalSerialPortInformation!} function. Locally
connected or network sensors can also be automatically recognised using
the \passthrough{\lstinline!list\_sensors!} function. Once connected,
these are then converted into a usable data source using the
\passthrough{\lstinline!MRPReadingSource!} module. This automatically
recognises the type of sensor and generated an
\passthrough{\lstinline!MRPReading!} instance with the measured values
of the sensor.

>>>>

Der Shimming-Prozess ist ein entscheidender Schritt bei der
Magnetresonanztomographie (MRT), um homogene Magnetfelder für präzise
Bildgebung zu gewährleisten. Shimming korrigiert Unregelmäßigkeiten im
statischen Magnetfeld, die durch äußere Einflüsse oder interne
Systemfehler entstehen können. Dieser Prozess optimiert die
Feldhomogenität, was für hochauflösende und artefaktfreie Bilder
entscheidend ist.

Die Quellen für den Shimming-Prozess können Hardware- und
Software-basiert sein. Hardware-Shimming beinhaltet den Einsatz von
Gradienten- und Radiofrequenzspulen, die gezielt platziert werden, um
das Magnetfeld auszurichten. Software-Shimming hingegen verwendet
Algorithmen, um die Steuerparameter des MRT-Systems anzupassen und die
Homogenität zu verbessern.

Forschungspublikationen wie ``Shimming Techniques in Magnetic Resonance
Imaging'' (DOI: 10.1007/978-1-4939-2815-6\_3) bieten detaillierte
Einblicke in verschiedene Shimming-Methoden und Techniken. Diese
Fortschritte in der Shimming-Technologie tragen dazu bei, die
diagnostische Genauigkeit und Bildqualität in der MRT erheblich zu
verbessern.

@@

The scope of the software library is to lay the foundation for the
systematic characterization of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customization possible at each step of the process.

The work aims to facilitate magnetic field characterization and improve
the exchange of data between different user groups. Complete
documentation, tutorials and tests will enable users to use the
framework efficiently and adapt it to their specific requirements.

The application of the developed framework for the characterization of
different magnets and the integration of magnetic field sensors serve as
practical applications and validation of the developed solution.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received. Since the presumed
\passthrough{\lstinline!primary!} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout branch
condition \passthrough{\lstinline!got pulse within 1000ms!} and this
becomes the \passthrough{\lstinline!primary!} sensor. This means that in
a chain of sensors there is exactly one
\passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
this automatically jumps to \passthrough{\lstinline!primary!} sensor
operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the
\passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
command. An important aspect of the implementation here was that there
is no numbering or sequence of the individual sensors. This means that
for the subsequent readout of the measurements, it is only important
that they are taken at the same interval across all sensors. The sensor
differentiation takes place later in the \gls{mrp}
\ref{software-readout-framework}-library by using the sensor \gls{uuid}.

@@

The software readout framework is the central software component that
was developed as part of this work. This software framework is intended
to provide a user-oriented data acquisition and analysis environment.
For this purpose, typical individual steps that occur in relation to
these tasks were implemented:

\begin{itemize}
\tightlist
\item
  Data acquisition - e.g.~from hardware sensors \ref{unified-sensor}
\item
  Storage - export of data in various open formats
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyze different data sets \ref{analysis}
\end{itemize}

All these possible task parts were divided into different blocks and
users were given the possibility of adding their own functionalities.

As the following, this concept is referred to as
\passthrough{\lstinline!user interaction points!}\ref{user-interaction-points}
and is explained in the following chapter.

\hypertarget{user-interaction-points}{%
\section{User Interaction Points}\label{user-interaction-points}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_library_module_high_level_overview.png}
\caption{MRP library module high level overview
\label{MRP_library_module_high_level_overview.png}}
\end{figure}

User interaction points represent the core concept of the developed
library and are intended to provide user-friendliness on the one hand
and the rapid development of own analysis and optimization algorithms on
the other. For this purpose, the library was divided into individual
modules, which are shown in the graphic
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types was developed and packed together in a extendable Python
library.

According to this concept, the user should be able to replace individual
components from this chain with their own modules without having to
worry about implementing other of these to make the project work.

\hypertarget{user-interaction-points-example}{%
\subsection{User Interaction Points
Example}\label{user-interaction-points-example}}

The following example shows the advantages of using the
\passthrough{\lstinline!User interaction points!}:

A project called
\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
implements a data analysis step and optimizes a magnetic field that is
as homogeneous as possible within a circular section using given
mechanical dimensions as input parameters of the magnets used. For this
purpose, a mutation of the magnet positions and rotations is performed.
The result is a list of positions for each magnet.

The
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
opensource project, can generate basic \gls{cad} drawings for \gls{mri}
magnets in a Hallbach configuration. To do this, the number of magnets
and additional parameters for the properties of the \gls{cad} model to
be created are passed to the function provided as input parameters using
a \gls{json} file. The result is then an
\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} based 3D model of
the magnet holder.

As a result, there are two projects which are both suitable for the task
of optimizing and creating Hallbach magnets for \gls{mri} applications.
However, their data structures are not compatible with each other.
However, they are executed manually one after the other in order to
obtain a final result.

The library created is intended to solve one problem by providing
standardized and flexible data structures for use with this form of
magnetic field data. On the other hand, by separating the processing
pipeline into defined sub-steps, it should be possible to make
individual modules and as a result functionalities interchangeable by
the user.

The implementation of the same functionalities looks as follows after
using the library:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Create a static set of magnets}
\end{enumerate}

The input parameters of the
\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. We assume ideal magnets here. However, it should
also be possible to import field data in a more measured form later on.
Using the DataAquisition sub-step, it is possible to generate any number
of ideal magnets.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{Add custom analysis processing step}
\end{enumerate}

Next, the user creates his own analysis step in order to be able to call
up its functions. In the case of the
\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
project, the function signature of the start function must be changed.
This receives the result of the previous step, in this case the
generated magnet data. By optionally setting meta data in the universal
bilbiothekt data type, constants can be replaced in the analysis
function and made dynamically configurable. The return result also
corresponds to this data type so that subsequent steps are compatible
and contains the magnet data with modified position and rotation data.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  \textbf{Generate fabrication data}
\end{enumerate}

The last step is to call up the
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
project, which creates the \gls{cad} model of the magnet holder. The
data can also be exported as files here. To make the project compatible,
the function signatures are also adapted here. In this case, more
changes are required, as the configuration file is loaded from the file
system. This logic must be removed in order to use the added meta data
in the input parameter instead.

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly. This also fulfills the goal of
making individual user-created algorithms interchangeable. If the user
now wishes to use a different \gls{cad} algorithm instead of the
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
the other steps can simply be preserved.

The individual modules and their functions are explained in detail in
the following chapters.

@@

In order to realise the concept of user interaction points, the library
was divided into different modules. These can be divided into two main
categories:

@@

In each of these categories there are then several sub-categories
divided into User Interaction Points. An overview of these is given in
the subchapters as the following. There are also introductory examples
which provide an overview of the basic functions in the
\passthrough{\lstinline!Examples!}\ref{examples} section, as well as
further examples in the online
documentation\cite{MagneticReadoutProcessingReadTheDocs}.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!additional\_data!} - Additional user-defined
  metadata
\item
  \passthrough{\lstinline!data!} - Measured values with value and
  measured value \gls{uuid}
\item
  \passthrough{\lstinline!measurement\_config!} - Information about the
  sensor used for measurement
\end{itemize}

@@

Each connected sensor is accessed via the text-based \gls{cli}, this is
initially the same for each sensor. The only identification feature is
the sensor \gls{uuid} by using the \passthrough{\lstinline!id!} command
of the sensor \gls{cli}.

@@

Immediately after starting the \passthrough{\lstinline!MRPProxy!}, the
\gls{uuid}s of all locally connected sensors are read out. These are
stored together with the class instance of the
\passthrough{\lstinline!MRPHal!} module in a \gls{lut}. This makes it
possible to address a sensor directly using its \gls{uuid}.

@@

To realize this, a \gls{lut} was created in the previous steps, which
contains information regarding
\passthrough{\lstinline!requested capability!} -\textgreater{}
\passthrough{\lstinline!sensor!}-\gls{uuid} -\textgreater{}
\passthrough{\lstinline!physical sensor!} and allows the commands to be
routed.

@@

The \passthrough{\lstinline!extend commands using an id parameter!}
strategy is used for different sensors. Each command is extended on the
\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} by another
\gls{uuid} parameter, according to the following scheme:

@@

This allows the host to address individual sensors directly via their
specific \gls{uuid}.

@@

In general, a sensor can be connected using its specific system path or
the sensor-\gls{uuid} via the
\passthrough{\lstinline!MRPHalSerialPortInformation!} function. Locally
connected or network sensors can also be automatically recognised using
the \passthrough{\lstinline!list\_sensors!} function. Once connected,
these are then converted into a usable data source using the
\passthrough{\lstinline!MRPReadingSource!} module. This automatically
recognises the type of sensor and generated an
\passthrough{\lstinline!MRPReading!} instance with the measured values
of the sensor.
